Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-29 paper/paper.tex
Tweaked Intro
Started Goals and Objectives section

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images, e.g. with low contrast, inadequate lighting, out of
focus, cluttered visual arrangements, provide inadequate input for automated
image analysis and machine learning algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (pixels/inch) is needed; thus
requiring the ability to identify and measure rulers in the images.
Many specimen collections do include Darwin Core metadata, detailing
specimen taxon, geographic location, and several other descriptive aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods to examine thousands of images
to determine if, for instance, a specific fish grows to different lengths
in different ecosystems.

Since the digital collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible. Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
As a step towards improving metadata in specimen research image collections, members of the Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digital specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
were  applied to a set of 7,247
images drawn from the Illinois Natural History Survey (INHS) Collection.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

@@

species, habitats and ecosystems, and for food the industry, in the

@@

fish image analysis followed the general trends in the field.

@@

of fish based on color and texture features and used a multi-class support

@@

Component Analysis, and derived a linear model from these four features

@@

extracted by the CNN in supervised deep learning. They achieved 90\%

@@

Network (CNN), data fitting, and ruler detection/measurement

@@

measurement by machine visions efforts.

@@

Tappi et al.~\cite{Tappi2017ComputerVS} assees the freshness of frozen

@@

>>>>

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images, e.g. with low contrast, inadequate lighting,
out-of-focus or cluttered visual arrangements, provide inadequate input
for automated
image analysis and machine learning algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (pixels/inch) is needed; thus
requiring the ability to identify and measure rulers in the images.
Many specimen collections do include Darwin Core metadata, detailing
specimen taxon, geographic location, and several other descriptive aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods to examine thousands of images
to determine if, for instance, a specific fish grows to different lengths
in different habitats.

Since the digital collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible. Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
As a step towards improving metadata in specimen research image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
were  applied to a set of 7,247
images drawn from the Illinois Natural History Survey (INHS) Collection.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

@@

species, habitats and ecosystems, and for the seafood industry, in the

@@

fish image analysis have followed the general trends in the AI field.

@@

of fish based on color and texture features and a multi-class support

@@

Component Analysis, and derived a linear model

@@

extracted by the CNN. They achieved 90\%

@@

Network (CNN), data fitting, and a ruler detection/measurement

@@

measurement efforts that utilize machine vision.

@@

Tappi et al.~\cite{Tappi2017ComputerVS} assess the freshness of frozen

@@

Digitized specimen collections offer numerous outstanding opportunities
for new scientific studies and discoveries.

The amount of data is immense, with image collections containing 10,000's
of entries. These discoveries will only be possible
with computational techniques that can process this vast amount of data.

These image-based computational techniques are hindered by both poor
image quality and the lack of high-quality and pertinent metadata.

For example, a study may require images that contain only one fish with a
given level of lighting and contrast. Additionally, performing quantitative
investiations into the morphology of the specimens requires knowing
the physical scale of the images, i.e.~pixels/inch.

Given the many thousands of images that have and will be acquired of
biological specimens, it is infeasible to generate the needed metadata
via manual, i.e. via human input, methods.  It is critical to deploy
computational techniques that will automate the process of generating
the pertinent metatdata that is essential for downstream analyses and
studies.

In order to address the need for fish specimen image metadata that can
support scientific investigations we have begun the deployment of
both off-the-shelf and custom-written software that automatically
generates a variety of metadata from a publicly-available biological
image repository.  The types of metadata being produced are related
to image quality, content and scale, and should provide the information
necessary for quantitative studies of the digitized specimens.
